\documentclass[11pt]{article}
\input{_preamble}

\title{\textbf{Data plan}\\
\large Memo 05}
\author{Bloomsbury Tech -- Agentic Payments Hackathon Build}
\date{April 25, 2026}

\begin{document}
\maketitle

\textbf{Date:} 2026-04-25

\section{Primary source: Base L2 + x402}
x402 facilitator addresses on Base are public. Coinbase Developer Platform publishes them. Pull recent transactions interacting with these facilitators \textbackslash{}\$\textbackslash{}to\textbackslash{}\$ agent-positive class. Pull sampled regular EOAs \textbackslash{}\$\textbackslash{}to\textbackslash{}\$ human-baseline class.

\textbf{Volume target:} 100k transactions for the demo. Stablecoin transaction volume hit \textbackslash{}\$33T in 2025 (+72\% YoY); agent-driven Layer 2 spikes of 10,000\% in early 2026 --- should be plenty.

\section{Cofounder action}
Cofounder is pulling Coinbase data. Confirm format: ideally raw transaction rows with \code{(block_number, block_time, from, to, value, gas_used, gas_price, input_data_or_method_id, success)}. CSV or parquet works; JSONL OK.

If Coinbase access is API-direct: \code{cdp.coinbase.com/api/v2/networks/base/transactions} style.

\section{Schema we standardise on}
\begin{lstlisting}
columns = [
    "block_number",   # int
    "block_time",     # datetime UTC
    "tx_hash",        # str
    "from_addr",      # str (lowercased)
    "to_addr",        # str (lowercased; contract or EOA)
    "value_wei",      # int (native ETH)
    "value_usd",      # float (token-aware, post-decode)
    "gas_used",       # int
    "gas_price_gwei", # float (gwei)
    "method_id",      # str (4-byte selector hex, or "0x" for native transfer)
    "success",        # bool
    "is_x402",        # bool -- interacted with known facilitator
    "facilitator",    # str | None
]
\end{lstlisting}
Stored as parquet at \code{data/raw/base_<date>.parquet}.

\section{Labels}
\begin{itemize}
  \item \textbf{Positive (agent):} addresses appearing on x402 facilitator interactions, or known agent-deployer addresses (Coinbase publishes a list).
  \item \textbf{Negative (human):} EOAs in the same time window with no x402 interaction, no contract creation, < 100 tx/day.
  \item \textbf{Unknown:} the rest. Treat as test set.
\end{itemize}
This is weak supervision. Good enough for the demo.

\section{Synthetic fallback (always-on)}
\code{src/ingest/synthetic.py} --- policy library generating ground-truth-labelled traffic:

\begin{center}
\begin{tabular}{ll}
\toprule
Policy & Behaviour \\
\midrule
\code{human_random} & Poisson arrivals (\textbackslash{}\$\textbackslash{}lambda\textbackslash{}\$=4/day), value lognormal(\textbackslash{}\$\textbackslash{}mu\textbackslash{}\$=4, \textbackslash{}\$\textbackslash{}sigma\textbackslash{}\$=1.5), high counterparty diversity, time-of-day human curve \\
\code{agent_arb_deterministic} & High-freq cron (every 60--90s), tight gas (within 1 gwei), 2--3 counterparties only, uniform across 24h \\
\code{agent_payment_bot} & Bursty (10 tx in 30s, then quiet), small fixed value, single counterparty per burst \\
\code{agent_compromised} & Starts as \code{agent_payment_bot}, drifts: gas spikes, value spikes, new counterparty after t=8h \\
\code{collusion_ring} & 5--10 wallets coordinating: trades within 60s of each other, shared counterparties \\
\bottomrule
\end{tabular}
\end{center}

Output matches the Base schema above + a sidecar \code{<run>_labels.parquet} with \code{(addr, policy, role)}.

\section{Demo data flow}
\begin{lstlisting}
data/synthetic/run1.parquet  (or data/raw/base_*.parquet when ready)
    
src.features.fingerprint
    
data/processed/features.parquet  (per-wallet rows, 30-50 cols)
    
src.models.cluster + src.models.score
    
data/processed/clusters.parquet, scores.parquet
    
src.viz.umap -> results/headline_figure.png
\end{lstlisting}
\section{Risk: real Base volume thinner than expected}
Mitigation: synthetic generator is the primary path; real data layered in if we have time. Saturday's pitch can demo on synthetic with real-data validation as a "and the same pipeline runs on 100k Base transactions" closer.

\end{document}
