\documentclass[11pt]{article}
\input{_preamble}

\title{\textbf{Synthetic Agent Traffic Generator -- Design and Validation}\\
\large Memo 07 -- Empirically Validated}
\author{Bloomsbury Tech -- Agentic Payments Hackathon Build}
\date{April 25, 2026}

\begin{document}
\maketitle

\begin{abstract}
We synthesise five labelled wallet policies to provide ground truth before
real Base data lands. This memo specifies the generators and validates that
the resulting per-wallet behavioural fingerprints separate by policy in
feature space. Code: \code{src/ingest/synthetic.py}; validation:
\code{experiments/synthetic_separation.py}; primary result: silhouette
0.35, 5-fold RF accuracy 99.6\%, macro-F1 0.997. Hypothesis H5 supported
with effect size well above pre-registered threshold.
\end{abstract}

\section{Why synthetic-first}

We control ground truth. Every wallet has a known policy label, so UMAP
separation, anomaly recall, and clustering precision become measurable
rather than anecdotal. Real Base data layers in for credibility on Saturday
(memos 12, 16); the pipeline must work without it.

\section{Policies}

Each policy is a stochastic generator producing transactions for one wallet
over a time window. Output rows match the canonical schema in memo 05.

\subsection*{\code{human_random}}
\begin{itemize}
  \item Inter-arrival: $\mathrm{Exponential}(\lambda = 1/(6\text{h}))$,
    $\approx 4$ tx/day.
  \item Value: $\mathrm{Lognormal}(\mu=4, \sigma=1.5)$ USD, clipped
    $[1,\ 50{,}000]$.
  \item Counterparties: drawn from human-counterparty pool, repeat
    probability 0.3.
  \item Time-of-day: rejection sampled against a daytime-weighted curve
    (peaks 10--14, 19--22 local).
  \item Gas price: $\mathrm{Normal}(\text{median basefee}, \sigma=10\
    \text{gwei})$ -- humans don't optimise.
  \item Method: 60\% native transfer, 30\% ERC-20 transfer, 10\% misc
    contract.
\end{itemize}

\subsection*{\code{agent_arb_deterministic}}
\begin{itemize}
  \item Inter-arrival: deterministic period 60--90s with $\pm 5$\% jitter.
  \item Value: tight band $[50,\ 200]$ USD.
  \item Counterparties: 2--3 fixed addresses (DEX router, token contract).
  \item Time-of-day: uniform 24h.
  \item Gas price: $\text{median basefee} + \mathrm{Uniform}(0, 1\ \text{gwei})$
    -- pathologically tight.
  \item Method: same 4-byte selector $>95$\% of calls.
\end{itemize}

\subsection*{\code{agent_payment_bot}}
\begin{itemize}
  \item Inter-arrival: bursty -- Poisson cluster process. Burst arrivals
    $\mathrm{Exponential}(\lambda=1/4\text{h})$; within burst
    $\mathrm{Poisson}(\text{rate}=10/\text{min})$ for $\approx 30$s.
  \item Value: fixed payment amount with $\pm 2$\% noise.
  \item Counterparties: 1 per burst (recipient), drawn from a small pool of 20.
  \item Time-of-day: skewed toward business hours but still mostly uniform.
  \item Gas: tight, +20\% over basefee for speed.
  \item Method: ERC-20 transfer dominant.
\end{itemize}

\subsection*{\code{agent_compromised}}
\begin{itemize}
  \item \textbf{Phase 1} ($t < 8$h): identical to \code{agent_payment_bot}.
  \item \textbf{Phase 2} ($t \geq 8$h): drift behaviours
  \begin{itemize}
    \item Counterparty pool replaced with new addresses (exfiltration target).
    \item Value distribution shifts: rare large transfers ($>10\times$ normal)
      appear.
    \item Gas spikes: 5$\times$ burst rate, gas price 3$\times$ normal.
    \item Method-id distribution adds a new selector (\code{approve} to
      malicious contract).
  \end{itemize}
\end{itemize}

This is the \textbf{headline detection target}. The composite score should
rise from low to critical across the drift.

\subsection*{\code{collusion_ring}}
\begin{itemize}
  \item 5--10 wallets sharing one coordinator.
  \item Each wallet: light independent activity $\sim$ \code{human_random}.
  \item \emph{Plus} coordinated bursts: every 2--4 hours the ring trades at
    near-simultaneous timestamps (within 60s) on shared counterparty.
  \item Detection target for the clusterer: tight clustering; individually
    they look benign.
\end{itemize}

\section{API}

\begin{lstlisting}[language=Python]
from src.ingest.synthetic import generate

txs, labels = generate(
    n_human=100,
    n_agent_arb=40,
    n_agent_payment=40,
    n_agent_compromised=10,
    n_collusion_rings=2,        # each = 5-10 wallets
    duration_hours=24,
    seed=42,
)
# txs: pd.DataFrame matching base schema
# labels: pd.DataFrame [addr, policy, role, ring_id]
\end{lstlisting}

\section{H5 -- Policies separate in 36-feature space}

\begin{hypothesis}
The 36 per-wallet behavioural features (memo 08) discriminate the five
synthetic policies. Pre-registered thresholds: silhouette $\geq 0.20$ and
5-fold stratified random-forest accuracy $\geq 0.85$.
\end{hypothesis}

\begin{experiment}
Generate a 247-wallet dataset (\code{seed=17}, 24-hour window). Compute the
36-feature fingerprint per wallet, standardise, and evaluate two metrics:
(i) silhouette score on the 5-class label, and (ii) a stratified 5-fold
\code{RandomForestClassifier} (200 trees, default depth) reporting accuracy
and macro-F1. Code: \code{experiments/synthetic_separation.py}.
\end{experiment}

\begin{result}
Silhouette $= 0.345$. RF 5-fold accuracy $= 0.996 \pm 0.008$, macro-F1
$= 0.997$. Both metrics clear the pre-registered thresholds by a wide margin;
the policies are essentially linearly separable in this feature space, with
minor confusions only between \code{collusion_ring} and \code{human_random}
on isolated wallets (the ring's individual baseline is human-random by
design). Hypothesis supported.
\end{result}

\section{Quality bar (the demo slide)}

The synthetic data passes if:
\begin{enumerate}
  \item UMAP on behavioural fingerprints visibly separates
    \code{human_random} vs. agent policies. \emph{Verified by H5
    silhouette.}
  \item Composite scorer assigns critical/high to $\geq 80$\% of
    \code{agent_compromised} wallets after $t=12$h.
  \item Clusterer recovers $\geq 80$\% of \code{collusion_ring} membership at
    silhouette $\geq 0.4$.
\end{enumerate}

Items (2) and (3) are scorer/cluster-specific and validated via the live
dashboard; the embedding-space separation is the necessary precondition,
which H5 confirms.

\end{document}
