\documentclass[11pt]{article}
\input{_preamble}

\title{\textbf{Hackathon logistics}\\
\large Memo 09}
\author{Bloomsbury Tech -- Agentic Payments Hackathon Build}
\date{April 25, 2026}

\begin{document}
\maketitle

\textbf{Date:} 2026-04-25

\section{Schedule}
\begin{itemize}
  \item \textbf{Friday 7pm} --- Reception, rooftop overlooking London skyline. Networking. Selected candidates only.
  \item \textbf{Saturday 10am -- 8pm} --- Full-day build, central London. 10 hours.
\end{itemize}
\section{Theme}
AI agents that manage flow of money. Real-world problems: rent, invoicing, international payments, reconciliation.

\section{Prize}
First place = guaranteed YC interview with \textbf{Tom Blomfield} (YC Partner, Monzo founder).

\section{Judging signal}
Per Eugene's read: assessment is \textbf{founder potential via pitch}, not "best product". Pitch is \textbf{2 minutes}. Working demo is signal of velocity, not the artifact being judged.

\section{Implications}
\begin{enumerate}
  \item The pitch is the deliverable. Build supports the pitch.
  \item Spend \textbackslash{}\$\textbackslash{}geq\textbackslash{}\$1 hour rehearsing on Saturday afternoon.
  \item Optimise for \emph{one} killer slide (UMAP cluster plot with anomaly explanations) over a complete product.
  \item Frame as "Bloomsbury Tech" (existing ML lab with publications) not "we're a couple of guys with an idea". Credibility compounds with Blomfield.
  \item Skip vision; lead with the gap.
\end{enumerate}
\section{Reception strategy}
\begin{itemize}
  \item Goal: pressure-test the pitch on 2-3 fintech-savvy people. Listen for the part that makes their face register confusion or skepticism --- that's what to fix Saturday morning.
  \item Don't reveal the technical approach (UMAP, the polymarket asset reuse). Reveal the \emph{gap} (human-baseline fraud blindness).
  \item Look for potential cofounders if the cofounder bandwidth is short.
\end{itemize}

\end{document}
