\documentclass[11pt]{article}
\input{_preamble}

\title{\textbf{Dashboard demo}\\
\large Memo 11}
\author{Bloomsbury Tech -- Agentic Payments Hackathon Build}
\date{April 25, 2026}

\begin{document}
\maketitle

\textbf{Date:} 2026-04-25

\section{Product surface}
Working name: \textbf{Agentic Payment Risk Console}.

The previous dashboard was visually interesting but under-explained: it led with a scatterplot before telling the viewer what decision the product helps them make. The Polymarket dashboard pattern is better: overview cards, tabbed tables, badges, factor bars, and ranked queues. The redesigned app follows that pattern.

Single-screen analyst console:

\begin{itemize}
  \item Dataset switch: \textbf{Synthetic stress test} vs \textbf{Public x402 Base}.
  \item Executive readout: one paragraph that says what the current data proves and what it does not prove.
  \item Metrics: transactions, wallets scored, immediate queue, watchlist, and either compromise recall or recipient count.
  \item Triage tab: alert queue with wallet, score, tier, action, policy, tx count, concentration, and explanation.
  \item Selected case: wallet evidence card plus factor breakdown.
  \item Behaviour Map tab: UMAP fingerprint space, deliberately secondary to the triage queue.
  \item Coordination tab: wallet graph and cluster table.
  \item Model Evidence tab: factor distribution so judges can see this is not an LLM vibes classifier.
\end{itemize}
\section{Demo beat}
\begin{enumerate}
  \item "This is a triage console for agentic payment risk."
  \item Open on the Synthetic stress test. Show that deterministic agents, compromised drift, and collusion rings enter the queue while humans do not.
  \item Read the selected case explanation out loud: timing, method concentration, counterparty concentration, coordination.
  \item Switch to Public x402 Base. Say: "On real public x402 traffic today, we see watchlist behaviour but no high-severity fraud claim yet. That honesty is the point."
  \item Use the Coordination tab to make compromised-agent contagion concrete.
\end{enumerate}
\section{Dashboard commands}
\begin{lstlisting}
make demo
\end{lstlisting}
Equivalent explicit commands:

\begin{lstlisting}
python3 -m venv .venv
.venv/bin/python -m pip install --upgrade pip
.venv/bin/python -m pip install -e ".[dash,dev]"
.venv/bin/python -m src.pipeline
.venv/bin/python -m streamlit run src/viz/dashboard.py
\end{lstlisting}
Use \code{.venv/bin/python -m streamlit} rather than \code{streamlit} so the shell does not need a global Streamlit command.

\end{document}
