\documentclass[11pt]{article}
\input{_preamble}

\title{\textbf{Public data collection}\\
\large Memo 12}
\author{Bloomsbury Tech -- Agentic Payments Hackathon Build}
\date{April 25, 2026}

\begin{document}
\maketitle

\textbf{Date:} 2026-04-25

\section{Easy-ish data collected}
No API keys needed.

\begin{enumerate}
  \item \textbf{x402.watch facilitator directory}
\end{enumerate}
\begin{itemize}
  \item Collected into \code{data/raw/x402_facilitators.parquet}.
  \item Tracked sample: \code{data/raw/sample_x402_facilitators.csv}.
  \item Use: facilitator URL list, public metadata, quick target list for \code{/supported} probes.
  \item Source: https://www.x402.watch/facilitators
\end{itemize}
\begin{enumerate}
  \item \textbf{Coinbase x402 facilitator addresses}
\end{enumerate}
\begin{itemize}
  \item Collected into \code{data/raw/x402_addresses.parquet}.
  \item Tracked sample: \code{data/raw/sample_x402_addresses.csv}.
  \item Use: Coinbase address watchlist for Base Blockscout queries.
  \item Source: https://x402.watch/facilitator/coinbase
\end{itemize}
\begin{enumerate}
  \item \textbf{OpenX402 \code{/supported} endpoint}
\end{enumerate}
\begin{itemize}
  \item Collected into \code{data/raw/x402_supported_probe.parquet}.
  \item Found active Base signer \code{0x97316FA4730BC7d3B295234F8e4D04a0a4C093e8} and Base USDC asset \code{0x833589fCD6eDb6E08f4c7C32D4f71b54bdA02913}.
  \item Source: https://facilitator.openx402.ai/supported
\end{itemize}
\begin{enumerate}
  \item \textbf{Base Blockscout no-key txlist}
\end{enumerate}
\begin{itemize}
  \item Collected into \code{data/raw/base_facilitator_txlist.parquet}.
  \item Normalized into \code{data/processed/real_x402_base.parquet}.
  \item Cooked payment-only rows into \code{data/processed/real_x402_payments.parquet}.
  \item Tracked samples:
  \item \code{data/processed/sample_real_x402_base.csv}
  \item \code{data/processed/sample_real_x402_payments.csv}
  \item \code{data/processed/sample_real_x402_scores.csv}
  \item Source: https://base.blockscout.com/api
\end{itemize}
\section{Current pull summary}
At first pull:

\begin{itemize}
  \item 7,512 Base facilitator-address transactions.
  \item 437 decoded x402/EIP-3009 USDC payment rows.
  \item 116 unique payer wallets.
  \item 19 unique recipient wallets.
  \item 116 payer wallets cooked through the scorer: 65 medium, 51 low, 0 high.
\end{itemize}
We decode \code{0xe3ee160e} calls to Base USDC as EIP-3009-style \code{transferWithAuthorization} rows:

\begin{itemize}
  \item payer address
  \item recipient address
  \item USDC amount
  \item validity window
  \item authorization nonce
  \item facilitator/signer address
\end{itemize}
This is the first real-data overlay for the synthetic demo.

Committed artifacts for cofounder access:

\begin{itemize}
  \item \code{data/raw/x402_facilitators.parquet}
  \item \code{data/raw/x402_addresses.parquet}
  \item \code{data/raw/x402_supported_probe.parquet}
  \item \code{data/processed/real_x402_base.parquet}
  \item \code{data/processed/real_x402_payments.parquet}
  \item \code{data/processed/real_x402_features.parquet}
  \item \code{data/processed/real_x402_scores.parquet}
  \item \code{data/processed/real_x402_embedding.parquet}
\end{itemize}
The larger raw Blockscout txlist remains ignored and reproducible via \code{python -m src.ingest.public_x402}.

\section{Commands}
\begin{lstlisting}
python -m src.ingest.public_x402
python -m src.pipeline_public
\end{lstlisting}
\code{src.ingest.public_x402} fetches and normalizes public data. \code{src.pipeline_public} cooks it through the same feature/scoring/embedding stack used for the synthetic demo.

\section{Not easy today / cofounder queue}
\begin{enumerate}
  \item \textbf{Dune x402 dashboards}
\end{enumerate}
\begin{itemize}
  \item Likely useful for volume and aggregate trend, but requires either manual dashboard export or Dune API key.
\end{itemize}
\begin{enumerate}
  \item \textbf{BigQuery Blockchain Analytics}
\end{enumerate}
\begin{itemize}
  \item Good for broader Base/Ethereum baseline, but requires GCP auth/project setup and table-name confirmation.
\end{itemize}
\begin{enumerate}
  \item \textbf{BaseScan / Etherscan v2}
\end{enumerate}
\begin{itemize}
  \item Easy technically, but needs API key for stable higher-volume pulls.
\end{itemize}
\begin{enumerate}
  \item \textbf{Forta alerts}
\end{enumerate}
\begin{itemize}
  \item Good weak labels for compromised/exploit wallets, but needs alert taxonomy work before cooking.
\end{itemize}
\begin{enumerate}
  \item \textbf{x402scan internal API}
\end{enumerate}
\begin{itemize}
  \item Public page is visible, but easy API endpoint was not obvious from a quick probe. Worth inspecting in browser/devtools if more x402-specific history is needed.
\end{itemize}

\end{document}
